---
title: "PSY471 Final Project Model Analysis"
author: "Ruoqi Huang"
date: "22/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(rtdists)
library(sciplot)
library(ggsignif)
library(ggpubr)
```


#Descriptive statistics

```{r}
ddm <- read.csv("/Users/athenahuang/Downloads/ddm_parameters-4.csv")
data1 <- read.csv("/Users/athenahuang/Downloads/data-2.csv")
ddm
data1
```

Distribution for the data-2
```{r}
hist(data1$rt)
rt_density <- density(data1$rt)
plot(rt_density)
table(data1$response)
table(data1$match)
table(data1$pair_type)
```

Distribution for the ddm parameter
```{r}
hist(ddm$v)
v_density <- density(ddm$v)
plot(v_density)
```
Subset for each participant on their performance
```{r}
#subset(ddm, subj_idx == "0")
#subset(data1, subj_idx == "0")
ddm_match <- subset(ddm, match == "match")
ddm_good_match <- subset(ddm_match, pair_type == "good")
ddm_mismatch <- subset(ddm, match == "mismatch")
ddm_good_mismatch <- subset(ddm_mismatch, pair_type == "good")
ddm_con_match <- subset(ddm_match, pair_type == "confusable")

ddm_mismatch <- subset(ddm, match == "mismatch")
ddm_con_mismatch <- subset(ddm_mismatch, pair_type == "confusable")
```


```{r}
summary(ddm_good_mismatch$t)
t.test(ddm_good_mismatch$t, ddm_good_match$t)
t.test(ddm_con_mismatch$t, ddm_con_match$t)
t.test(ddm_con_mismatch$t, ddm_good_mismatch$t)
t.test(ddm_con_match$t, ddm_good_match$t)
```

```{r}
summary(ddm_good_mismatch$v)
#t.test(ddm_good_mismatch$v, ddm_good_match$v)
t.test(ddm_con_mismatch$v, ddm_con_match$v)
t.test(ddm_con_mismatch$v, ddm_good_mismatch$v)
t.test(ddm_con_match$v, ddm_good_match$v)

```
```{r}
summary(ddm_good_mismatch$a)
t.test(ddm_good_mismatch$a, ddm_good_match$a)
t.test(ddm_con_mismatch$a, ddm_con_match$a)
t.test(ddm_con_mismatch$a, ddm_good_mismatch$a)
t.test(ddm_con_match$a, ddm_good_match$a)
```

```{r}
summary(ddm_good_mismatch$t)
t.test(ddm_good_mismatch$t, ddm_good_match$t)
t.test(ddm_con_mismatch$t, ddm_con_match$t)
t.test(ddm_con_mismatch$t, ddm_good_mismatch$t)
t.test(ddm_con_match$t, ddm_good_match$t)
```


```{r}
data1_match <- subset(data1, match == "match")
data1_mismatch <- subset(data1, match == "mismatch")
data1_con_mismatch <- subset(data1_mismatch, pair_type == "confusable")
data1_good_mismatch <- subset(data1_mismatch, pair_type == "good")
data1_con_match <- subset(data1_match, pair_type == "confusable")
data1_good_match <- subset(data1_match, pair_type == "good")
```

```{r}
summary(data1_con_mismatch$response)
summary(data1_con_match$response)
summary(data1_good_match$response)
summary(data1_good_mismatch$response)
varsum <- c(summary(data1_con_mismatch$response),summary(data1_con_match$response),summary(data1_good_match$response),summary(data1_good_mismatch$response),summary(data1_con_mismatch$rt),summary(data1_con_match$rt),summary(data1_good_match$rt),summary(data1_good_mismatch$rt),summary(ddm_con_mismatch$v),summary(ddm_con_match$v),summary(ddm_good_match$v),summary(ddm_good_mismatch$v),summary(ddm_con_mismatch$a),summary(ddm_con_match$a),summary(ddm_good_match$a),summary(ddm_good_mismatch$a),summary(ddm_con_mismatch$t),summary(ddm_con_match$t),summary(ddm_good_match$t),summary(ddm_good_mismatch$t))
write.csv(varsum, file = 'varsum.csv')
```


```{r}
library(ggplot2)
library(ggsignif)

data <- data.frame(
  Response_Type=c("GM","Gmis","CM","Cmis"),
  Accuracy=c(mean(data1_good_match$response), mean(data1_good_mismatch$response), mean(data1_con_match$response), mean(data1_con_mismatch$response)),
  sd=c(se(data1_good_match$response), se(data1_good_mismatch$response), se(data1_con_match$response), se(data1_con_mismatch$response))
)

# Most basic error bar
acc <- ggplot(data) +
    geom_bar(aes(x=Response_Type, y=Accuracy), stat="identity", fill="grey", alpha=0.7) +
    geom_errorbar( aes(x=Response_Type, ymin=Accuracy-sd, ymax=Accuracy+sd), width=0.2, colour="black", alpha=0.9, size=0.5)+geom_line(data=tibble(x=c(1,3),y=c(1,1)),aes(x=x,y=y))+geom_text(data=tibble(x=2,y=1.125),aes(x=x,y=y,label="*"),size=8)
acc
```
```{r}
sd(data1_con_match$response)
sd(data1_good_match$response)
sd(data1_con_mismatch$response)
sd(data1_good_mismatch$response)
t.test(data1_con_mismatch$response, data1_con_match$response)
t.test(data1_con_mismatch$response, data1_good_mismatch$response)
t.test(data1_con_match$response, data1_good_match$response)
t.test(data1_good_mismatch$response, data1_good_match$response)
```


```{r}
sd(data1_con_match$rt)
sd(data1_good_match$rt)
sd(data1_con_mismatch$rt)
sd(data1_good_mismatch$rt)
t.test(data1_con_mismatch$rt, data1_con_match$rt)
t.test(data1_con_match$rt, data1_good_match$rt)
t.test(data1_con_match$rt, data1_good_mismatch$rt)
t.test(data1_con_mismatch$rt, data1_good_match$rt)
t.test(data1_con_mismatch$rt, data1_good_mismatch$rt)
t.test(data1_good_mismatch$rt, data1_good_match$rt)
```

```{r}
t.test(data1_con_mismatch$response, data1_con_match$response)
t.test(data1_con_match$response, data1_good_match$response)
t.test(data1_con_match$response, data1_good_mismatch$response)
t.test(data1_con_mismatch$response, data1_good_match$response)
t.test(data1_con_mismatch$response, data1_good_mismatch$response)
t.test(data1_good_mismatch$response, data1_good_match$response)
```

```{r}
data <- data.frame(
  Response_Type=c("GM","Gmis","CM","Cmis"),
  Reaction_Time=c(mean(data1_good_match$rt), mean(data1_good_mismatch$rt), mean(data1_con_match$rt), mean(data1_con_mismatch$rt)),
  sd=c(se(data1_good_match$rt), se(data1_good_mismatch$rt), se(data1_con_match$rt), se(data1_con_mismatch$rt))
)
 
# Most basic error bar
rtime <- ggplot(data) +
    geom_bar(aes(x=Response_Type, y=Reaction_Time), stat="identity", fill="grey", alpha=0.7) +
    geom_errorbar( aes(x=Response_Type, ymin=Reaction_Time-sd, ymax=Reaction_Time+sd), width=0.2, colour="black", alpha=0.9, size=0.5)+  geom_line(data=tibble(x=c(2,4),y=c(0.8,0.8)),aes(x=x,y=y))+geom_line(data=tibble(x=c(1,3),y=c(0.65,0.65)),aes(x=x,y=y))+geom_text(data=tibble(x=2,y=0.66),aes(x=x,y=y,label="***"),size=4)+geom_text(data=tibble(x=3,y=0.82),aes(x=x,y=y,label="***"),size=4)
rtime
```


```{r}
xtabs(~match+pair_type, ddm)
aggregate(v~match+pair_type,ddm, mean)

model.1 <- aov(v~match+pair_type,ddm)
summary(model.1)
```

```{r}
t.test(ddm_con_match$a, ddm_con_mismatch$a)
t.test(ddm_con_match$a, ddm_good_match$a)
t.test(ddm_con_match$a, ddm_good_mismatch$a)
t.test(ddm_con_mismatch$a, ddm_good_match$a)
t.test(ddm_con_mismatch$a, ddm_good_mismatch$a)
t.test(ddm_good_match$a, ddm_good_mismatch$a)
```

```{r}

t.test(ddm_con_match$t, ddm_con_mismatch$t)
t.test(ddm_con_match$t, ddm_good_match$t)
t.test(ddm_con_match$t, ddm_good_mismatch$t)
t.test(ddm_con_mismatch$t, ddm_good_match$t)
t.test(ddm_con_mismatch$t, ddm_good_mismatch$t)
t.test(ddm_good_match$t, ddm_good_mismatch$t)
```

```{r}
sd(ddm_con_match$v)
sd(ddm_good_match$v)
sd(ddm_con_mismatch$v)
sd(ddm_good_mismatch$v)
t.test(ddm_con_match$v, ddm_con_mismatch$v)
t.test(ddm_con_match$v, ddm_good_match$v)
t.test(ddm_con_match$v, ddm_good_mismatch$v)
t.test(ddm_con_mismatch$v, ddm_good_match$v)
t.test(ddm_con_mismatch$v, ddm_good_mismatch$v)
t.test(ddm_good_match$v, ddm_good_mismatch$v)
```


```{r}
sd(ddm_con_match$a)
sd(ddm_good_match$a)
sd(ddm_con_mismatch$a)
sd(ddm_good_mismatch$a)
t.test(ddm_good_mismatch$a, ddm_good_match$a)
t.test(ddm_con_mismatch$a, ddm_con_match$a)
t.test(ddm_con_mismatch$a, ddm_good_mismatch$a)
t.test(ddm_con_match$a, ddm_good_match$a)
```


```{r}
data <- data.frame(
  Response_Type=c("GM","Gmis","CM","Cmis"),
  a=c(mean(ddm_good_match$a), mean(ddm_good_mismatch$a), mean(ddm_con_match$a), mean(ddm_con_mismatch$a)),
  sd=c(se(ddm_good_match$a), se(ddm_good_mismatch$a), se(ddm_good_mismatch$a), se(ddm_good_mismatch$a)))
 
# Most basic error bar
a_g <- ggplot(data) +
    geom_bar(aes(x=Response_Type, y=a), stat="identity", fill="grey", alpha=0.7) +
    geom_errorbar( aes(x=Response_Type, ymin=a-sd, ymax=a+sd), width=0.2, colour="black", alpha=0.9, size=0.5)+  geom_line(data=tibble(x=c(2,4),y=c(1.5,1.5)),aes(x=x,y=y))+geom_line(data=tibble(x=c(1,3),y=c(1.4,1.4)),aes(x=x,y=y))+geom_text(data=tibble(x=2,y=1.42),aes(x=x,y=y,label="***"),size=4)+geom_text(data=tibble(x=3,y=1.55),aes(x=x,y=y,label="***"),size=4)
a_g
```
```{r}
data <- data.frame(
  Response_Type=c("GM","Gmis","CM","Cmis"),
  v=c(mean(ddm_good_match$v), mean(ddm_good_mismatch$v), mean(ddm_con_match$v), mean(ddm_con_mismatch$v)),
  sd=c(se(ddm_good_match$v), se(ddm_good_mismatch$v), se(ddm_good_mismatch$v), se(ddm_good_mismatch$v)))
 
# Most basic error bar
v_g <- ggplot(data) +
    geom_bar(aes(x=Response_Type, y=v), stat="identity", fill="grey", alpha=0.7) +
    geom_errorbar( aes(x=Response_Type, ymin=v-sd, ymax=v+sd), width=0.2, colour="black", alpha=0.9, size=0.5)+  geom_line(data=tibble(x=c(1,3),y=c(1.9,1.9)),aes(x=x,y=y))+geom_text(data=tibble(x=2,y=2),aes(x=x,y=y,label="***"),size=4)+geom_line(data=tibble(x=c(1,2),y=c(1.55,1.55)),aes(x=x,y=y))+geom_text(data=tibble(x=1.5,y=1.6),aes(x=x,y=y,label="***"),size=4) + geom_line(data=tibble(x=c(2,4),y=c(2.1,2.1)),aes(x=x,y=y))+geom_text(data=tibble(x=3,y=2.15),aes(x=x,y=y,label="***"),size=4)
v_g
```



```{r}
data <- data.frame(
  Response_Type=c("GM","Gmis","CM","Cmis"),
  t=c(mean(ddm_good_match$t), mean(ddm_good_mismatch$t), mean(ddm_con_match$t), mean(ddm_con_mismatch$t)),
  sd=c(se(ddm_good_match$t), se(ddm_good_mismatch$t), se(ddm_good_mismatch$t), se(ddm_good_mismatch$t)))
 
# Most basic error bar
t_g <- ggplot(data) +
    geom_bar(aes(x=Response_Type, y=t), stat="identity", fill="grey", alpha=0.7) +
    geom_errorbar( aes(x=Response_Type, ymin=t-sd, ymax=t+sd), width=0.2, colour="black", alpha=0.9, size=0.5)
```

```{r}
ggarrange(rtime, acc,
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 1)
```
```{r}
ggarrange(v_g,                                                 # First row with scatter plot
          ggarrange(a_g, t_g, ncol = 2, labels = c("B", "C")), # Second row with box and dot plots
          nrow = 2, 
          labels = "A"                                        # Labels of the scatter plot
          ) 
```

```{r}
t_g
```

Descriptive
ANOVA(factorial design with interaction)
Interaction(plot)
post-hoc(t-test) -> interpretation

summary measure for participant
t-test(within-subject design)
  
Average Accuracy ->

Regression?
Expectation

Analyze
Interpret that
Think about the interpretation
```{r}
#individual performance overall

mean(subset(data1$response, data1$subj_idx==1, data1$match=="good match", data1$pair_type==""))
mean(subset(data1$response, data1$subj_idx==2))
mean(subset(data1$response, data1$subj_idx==3))
mean(subset(data1$response, data1$subj_idx==4))
mean(subset(data1$response, data1$subj_idx==5))
mean(subset(data1$response, data1$subj_idx==6))
mean(subset(data1$response, data1$subj_idx==7))
```
```{r}
with(data1, by(rt, match, mean))
```
```{r}
aggregate( response ~ subj_idx, data1, mean)
aggregate( response ~ match, data1, mean)
aggregate( response ~ pair_type, data1, mean)
```
```{r}
by_par <- data1 %>% group_by(match,pair_type) %>% summarise (x = mean(response), y=mean(rt))
match <- subset(by_par$y, by_par$match=="match")
mismatch <- subset(by_par$y, by_par$match=="mismatch")

hist(match,xlim=c(0.2,1),col='skyblue',border=F)
hist(mismatch,add=T,col=scales::alpha('red',.5),border=F)

xfit<-seq(min(match),max(match),length=40) 
yfit<-dnorm(xfit,mean=mean(match),sd=sd(match)) 
yfit <- yfit*diff(h$mids[1:2])*length(match) 
lines(xfit, yfit, col="blue", lwd=2)

xfit1<-seq(min(mismatch),max(mismatch),length=40) 
yfit1<-dnorm(xfit1,mean=mean(mismatch),sd=sd(mismatch)) 
yfit1 <- yfit1*diff(h$mids[1:2])*length(mismatch) 
lines(xfit1, yfit1, col="red", lwd=2)
by_par


```


```{r}
gmatch <- subset(by_par$y, by_par$pair_type=="good", by_par$match=="match")
cmatch <- subset(by_par$y, by_par$pair_type=="confusable", by_par$match=="match")
gmismatch <- subset(by_par$y, by_par$pair_type=="good", by_par$match=="mismatch")
cmismatch <- subset(by_par$y, by_par$pair_type=="confusable", by_par$match=="mismatch")

b <- min(c(gmatch,cmismatch))-0.001 # Set the minimum for the breakpoints
e <- max(c(gmatch,cmismatch)) # Set the maximum for the breakpoints
ax <- pretty(b:e, n = 12) # Make a neat vector for the breakpoints
ax


hgA <- hist(gmatch, breaks = 20, plot = FALSE) # Save first histogram data
hgB <- hist(cmismatch, breaks = 20, plot = FALSE) # Save 2nd histogram data

plot(hgA, col = "red") # Plot 1st histogram using a transparent color
plot(hgB, col = "blue", add = TRUE) # Add 2nd histogram using different color
```


```{r}
match <- subset(by_par$y, by_par$pair_type=="good")
mismatch <- subset(by_par$y, by_par$pair_type=="confusable")

hist(match,xlim=c(0.2,1),col='skyblue',border=F)
hist(mismatch,add=T,col=scales::alpha('red',.5),border=F)

xfit<-seq(min(match),max(match),length=40) 
yfit<-dnorm(xfit,mean=mean(match),sd=sd(match)) 
yfit <- yfit*diff(h$mids[1:2])*length(match) 
lines(xfit, yfit, col="blue", lwd=2)

xfit1<-seq(min(mismatch),max(mismatch),length=40) 
yfit1<-dnorm(xfit1,mean=mean(mismatch),sd=sd(mismatch)) 
yfit1 <- yfit1*diff(h$mids[1:2])*length(mismatch) 
lines(xfit1, yfit1, col="red", lwd=2)
```


```{r}
```

